\documentclass[letterpaper,11pt]{article}
% chktex-file 1
% chktex-file 8
% chktex-file 27

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom Commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeExperienceHeading}[3]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} {\small\textit{#2}} & #3 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Meghan Herbert} \\ \vspace{1pt}
    \small (845) 467-5820 $|$ \href{mailto:mkherbert@albany.edu}{\underline{mkherbert@albany.edu}} $|$
    \href{https://www.linkedin.com/in/meghan-herbert-7023162bb/}{\underline{linkedin.com/in/meghan-herbert-7023162bb}} $|$
    \href{https://github.com/sheebos}{\underline{github.com/sheebos}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University at Albany}{Aug. 2022 -- May 2026}
      {B.S. Electrical and Computer Engineering, Minor in Mathematics $|$ \textbf{GPA:} 3.2/4.0}
      {Albany, NY}
      \small{\item{
    {\textbf{Awards}: 2026 133rd Topical Symposium NYSS APS\@: Best Graduate Poster Award, Student Leadership Award 2025 -- UAlbany ECE Department, Best Project Showcase Day 2025 - UAlbany ECE Department, UAlbany Hackathon Best ECE Project 2024}\\
   }}

  \resumeSubHeadingListEnd

%----------- TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      {\textbf{Instrumentation}: High-vacuum chambers, Mass Spectrometry, Electrical Device Characterization Techniques}\\
      {\textbf{Languages}: Python, MATLAB, LaTeX, C, VHDL, Verilog, MIPS, Java}\\
      {\textbf{Tools}: Visual Studio Code, MATLAB, Autodesk Fusion, AutoCAD, Spyder}}}
    \end{itemize}

    %-----------PROJECTS-----------
    \section{Projects}
      \resumeSubHeadingListStart

      \resumeProjectHeading
        {\textbf{Cryogenic Characterization of MEMS Switches} $|$ UAlbany \& Menlo Micro}{Fall 2025 -- Spring 2026}
        \resumeItemListStart
          \resumeItem{Evaluated MEMS switch devices for cryogenic quantum-system applications, focusing on reduced heat dissipation compared to conventional relay-based switching.}
          \resumeItem{Performed dynamic response testing of MEMS cantilevers under room-temperature, liquid nitrogen, and high-vacuum conditions to characterize resonant frequency and damping behavior.}
          \resumeItem{Analyzed device performance before and after cryogenic exposure, comparing chipped and unchipped MEMS switches to assess environmental robustness and mechanical consistency.}
        \resumeItemListEnd
      \resumeProjectHeading
        {\textbf{Encapsulation Effects on MEMS Switches Resistance} $|$ UAlbany \& Menlo Micro}{Summer 2025}
        \resumeItemListStart
          \resumeItem{Investigated how varying gas-environment compositions affect MEMS RF switch contact resistance.}
          \resumeItem{Performed vacuum system operation, pressure and gas control, and automated test measurements.}
        \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{Helium Leak Detection for Semiconductor Applications} $|$ GlobalFoundries}{Spring 2026}
          \resumeItemListStart
            \resumeItem{Designed a thermistor-based Wheatstone bridge TCD array to detect helium leaks through differential voltage shifts caused by thermal conductivity changes.}
            \resumeItem{Integrated Arduino Due and Raspberry Pi data collection to process, display, and save sensor outputs.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{Wafer Defect Classification using Machine Learning}}{Spring 2026}
          \resumeItemListStart
            \resumeItem{Classified semiconductor wafer map defect patterns from the WM-811K dataset using CNN-based image classification and a Random Forest baseline.}
          \resumeItemListEnd


      \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeExperienceHeading
      {Undergraduate Research Assistant}{UAlbany CNSE}{June 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Research MEMS switch resistance and lifetime under varying encapsulation environments in collaboration with Menlo Microsystems and University at Albany.}
        \resumeItem{Operate a custom high-vacuum chamber to test temperature-dependency and gas-composition characterization.}
        \resumeItem{Develop hands-on experience with chamber isolation, environmental control, and data acquisition for MEMS switch characterization.}
        \resumeItem{Assisted in development of technical CAD drawings, related machining and assembled custom vacuum-system components for use in both overpressure systems and vacuum.}
      \resumeItemListEnd
    \resumeExperienceHeading
      {AVS Student Chapter - Secretary}{American Vacuum Society}{Spring 2026 -- Present}
      \resumeItemListStart
        \resumeItem{Coordinated local AVS conference support and student chapter events.}
      \resumeItemListEnd

    \resumeExperienceHeading
      {IEEE Student Branch - Vice President \& Director of ECE Affairs}{IEEE}{Fall 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Lead a large student engineering organization and coordinate events supporting ECE student engagement, professional development, and department outreach.}
      \resumeItemListEnd

    \resumeExperienceHeading
      {Peer Teacher, CNSE Learning Center}{UAlbany CNSE}{Fall 2023 -- Winter 2024}
      \resumeItemListStart
        \resumeItem{Provided academic support for 3 introductory ECE classes, helping students understand fundamental digital systems, introductory ECE concepts, and computer science foundations.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------AWARDS-----------
\end{document}
